On Secure Delegation of SampBQP with a Classical Client

### 2020-01-23 blind.tex
Make editorial changes

\Ethan{TODO Do some kinda intro to the section}

@@

\Ethan{This subsection is copied and pasted directly from the other QMPC paper and is kinda a mess}

We present the quantum full homomorphic encryption (QFHE) scheme, $\mathsf{QHE}=(\mathsf{QHE.keygen}, \mathsf{QHE.Enc}, \mathsf{QHE.Dec}, \mathsf{QHE.Eval})$ given in \cite{mahadev_qfhe} which allows the use of a classical client. Specifically, it has the following extra properties:
\begin{itemize}
	\item $\mathsf{QHE.Keygen}$ can be done classically.
	\item In the case where the plaintext is classical, $\mathsf{QHE.Enc}$ can be done classically.
\end{itemize}

@@

\subsection{Generalizing our delegation protocol using QFHE}

\Ethan{TODO intro}

Here's what the client should do.

>>>>

@@

We first present the quantum full homomorphic encryption (QFHE) scheme, $\mathsf{QHE}=(\mathsf{QHE.Keygen}, \mathsf{QHE.Enc}, \mathsf{QHE.Dec}, \mathsf{QHE.Eval})$ given in \cite{mahadev_qfhe} which allows the use of a classical client. Specifically, it has the following extra properties:
\begin{itemize}
	\item $\mathsf{QHE.Keygen}$ can be done classically.
	\item In the case where the plaintext is classical, $\mathsf{QHE.Enc}$ can be done classically.
\end{itemize}

@@

\subsection{Our Delegation Protocol}

Now we're ready to construct our delegation protocol.
